---
title: "projects & papers"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

### Associations Between Inflammatory Marker Profiles and Cognitive Functioning Paper

[found here](pdf/associationspaper.pdf).

### Machine-Type Communication for Maritime Internet of Things Paper

[found here](pdf/machinetypecommunication.pdf).

### Impact Evaluation of UC San Diego COVID Response Team Wellness and Job Satisfaction Project

[found here](pdf/impactevaluation.pdf).

### Evaluation of Risk Mitigation Behaviors among San Diegans Project

[found here](pdf/riskmitigation.pdf).

### Safety and Efficacy of the BNT162b2 mRNA Covid-19 Vaccine Project

[found here](pdf/vaccine.pdf).

### National Oceanic and Atmospheric Association Project

The National Oceanic and Atmospheric Association (NOAA) of the National Centers for Environmental Information (NCEI) provides public access to some weather data, including the GHCN (Global Historical Climatology Network)-Daily database of summary statistics from weather stations around the world. 

These data were accessed from the NOAA National Climatic Data Center, http://doi.org/10.7289/V5D21VHZ (Menne, M.J., I. Durre, B. Korzeniewski, S. McNeal, K. Thomas, X. Yin, S. Anthony, R. Ray, R.S. Vose, B.E.Gleason, and T.G. Houston, 2012: Global Historical Climatology Network - Daily (GHCN-Daily), Version 3.22).

```{r setup, message = FALSE, echo = FALSE}

library(tidyverse)
library(p8105.datasets)
library(plotly)

```

```{r import data, message = FALSE, echo = FALSE}

data("ny_noaa") 

```

```{r tidy data, message = FALSE}

set.seed(8) 

ny_noaa <-
  ny_noaa %>%
  sample_n(99999) %>%
  janitor::clean_names() %>% 
  drop_na() %>% 
  separate(col = date, 
           into = c("year","month", "day")) %>%
  mutate(across(.cols
                = c(year, month, day), as.integer)) %>%
  mutate(month = month.name[month]) %>%
  mutate(snow = as.numeric(snow),
         tmax = as.integer(tmax)/10,
         tmin = as.integer(tmin)/10)

```

#### Box Plot

```{r message = FALSE}

ny_noaa %>%
  mutate(month = 
           fct_reorder(month, tmin)) %>%
  group_by(year, month, id) %>%
  summarize(mean_tmin = mean(tmin)) %>%
  plot_ly(x = ~ month, 
          y = ~ round(mean_tmin, digits = 0), 
          color = ~ month, 
          alpha = 0.6,
          type = "box",
          colors = "inferno") %>%
  layout(
    title = 
      "Average Minimum Temperature per Month", 
    xaxis = list(title = "Month"),
    yaxis = list(title = "Mean Minimum Temperature (Celcius)")) 

```

#### Bar Plot

```{r warning = FALSE}

ny_noaa %>%
  count(snwd) %>% 
  filter(snwd > 0) %>% 
  plot_ly(x = ~ snwd, 
          y = ~ n, 
          type = "bar", 
          color = "inferno") %>%
  layout(
    title = 
      "Snow Depth Count (Snow Days Only)", 
    xaxis = list(title = "Snow Depth (mm)"),
    yaxis = list(title = "Count (n)"))

```

#### Scatter Plot

```{r scatter plot, message = FALSE}

ny_noaa %>%
  filter(year == 2010) %>%
  mutate(text_label = str_c("Max Temperature: ", tmax, 
                            ", Min Temperature: ", tmin, 
                            ", Date: ", month," ", day,", ", year)) %>%
  plot_ly(x = ~ tmin, 
          y = ~ tmax,
          alpha = 0.6,
          color = ~ month,
          colors = "inferno", 
          text = ~ text_label) %>%
  layout(title = "Minimum Temperature versus Maximum Temperature (2010)",
         xaxis = list(title = "Minimum temperature (Celcius)"),
         yaxis = list(title = "Maximum temperature (Celcius)"))

```

<br>
<center>

Click here to return to the [main](index.html) page.